Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2021-01-19 minimax.tex
candidate questions

Let $(x^{*},\bar{y}, \bar{\profile}, \bar{\w})$ be the current solution of the minimax regret, where $x^{*}$ is the minimax optimal alternative and $\bar{y}, \bar{\profile}, \bar{\w}$ the corresponding adversarial choices. 
The \strat{Pessimistic} strategy considers a set of $n + m$ candidate questions: one per agent, and one per rank \commentOC{Isn’t this $m-2$?}.
The candidate questions to the agents are chosen by extending the idea of \citet{Lu2011}, that priviledge learning about the relationship of $x^*$ and $\bar{y}$ to the other alternatives if possible.
The candidate questions to the chair are determined as in the Random strategy.
The Pessimistic strategy selects among these $n + m$ candidate questions one that leads to minimal regret in the worst case: for each question we compute the minimax regret for the two possible answers, considering a penalty terms depending on the kind of question, and choose the best according to (quasi-)$\leximax$. \Cref{sec:appendix} provides more details.

>>>>

Let $(x^{*},\bar{y}, \bar{\profile}, \bar{\w})$ be the current solution of the minimax regret, where $x^{*}$ is the minimax optimal alternative and $\bar{y}, \bar{\profile}, \bar{\w}$ the corresponding adversarial choices. 
The \strat{Pessimistic} strategy considers a set of $n + (m-2)$ candidate questions: one per agent, and one per rank (excluding the first and the last one which are known).
The candidate questions to the agents are chosen by extending the idea of \citet{Lu2011}, that priviledge learning about the relationship of $x^*$ and $\bar{y}$ to the other alternatives if possible.
The candidate questions to the chair are determined as in the Random strategy.
The Pessimistic strategy selects among these $n + m - 2$ candidate questions one that leads to minimal regret in the worst case: for each question we compute the minimax regret for the two possible answers, considering a penalty terms depending on the kind of question, and choose the best according to (quasi-)$\leximax$. \Cref{sec:appendix} provides more details.
